\documentclass[a4paper]{article}

\usepackage[ampersand]{easylist}
\usepackage[nottoc,numbib]{tocbibind}
\usepackage{hyperref}

\title{\href{https://datsoftlyngby.github.io/soft2020fall/resources/8af56d7d-assignment-01.pdf}{Assingment} 1}
\author{Jacob Borg}
\date{October 2020}

\begin{document}

\maketitle
\tableofcontents

\section{Task 1}
Find requirements of bachelor thesis. Write a \LaTeX -document explaining your
findings. Document your sources.

\subsection{Bachelor thesis requirements}

\subsubsection{Structure}
The Bachelor thesis should include: cover, table of content, main content (introduction, body, summary), references, and affidavit. The thesis might also include: list of abbreviations, list of figures, list of tables, list of symbols, appendix.\cite{unimannheim2014guidelines}

\noindent The thesis should include: title page, table of contents, vocabulary of main concepts, introduction, report part (scientific literature review, methodology, empirical data analysis), conclusions and proposals, list of references, summary, and annexes.\cite{mru2018requirements}

\noindent It is suggested that the thesis include: front page, title page, preface, table of content, abstract, summary, introduction, background, methods, results, discussion, conclusions, perspectives, bibliography, and appendix.\cite{au2020guidelines}

\subsubsection{References}
All references that has been quoted or cited in the text have to be included in the reference list.\cite{unimannheim2014guidelines}

\noindent It is important to give a reference when making statements from literature. Reference acknowledge the work of others, and provide information of the sources used.\cite{au2020guidelines}

\subsubsection{Length}
The content part of the thesis should span 20 to 35 pages. The thesis should be as short as possible, but as extensive as necessary, while still within this range.\cite{unimannheim2014guidelines}

\noindent The thesis should be between 40 and 50 pages, not including title page, table of content, and  list of references.\cite{mru2018requirements}

\noindent The thesis contains maximum 100 pages, not including front page, table of content, bibliography, appendix, figures, tables, and models.\cite{au2020guidelines}

\bibliographystyle{plain}
\bibliography{references}

\end{document}